---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# b2packagetessosbrn

<!-- badges: start -->
<!-- badges: end -->

Welcome to my first package - a very basic package that served as some great practice for a class assignment, and will likely be useful in the future as a package template.


The goal of b2packagetessosbrn is to house the `mean_sd()` function that creates new columns in your dataset that contain the mean and sd values for a group of interest, all while retaining the rest of the dataset as-is.

## Installation

b2packagetessosbrn is not yet on CRAN. But, you can download it from this repository using the following R command: 

``` r
# install.packages("devtools")
devtools::install_github("stat545ubc-2021/b2packagetessosbrn")
```

## Example Use

This is a basic example that shows you how to obtain the mean and sd values for body mass of all the penguins on a certain island from the palmerpenguins package:

```{r example}
library(b2package)
mean_sd(palmerpenguins::penguins, island, body_mass_g)
```

b2packagetessosbrn is useful because it allows those cleaning their datasets to have simple functions that provide useful columns without dealing with intermediate steps - hopefully will be expanded in the near future to include many more cleaning steps!

