---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# b2packagetessosbrn

<!-- badges: start -->
<!-- badges: end -->

The goal of b2package is to house mean_sd() that creates new columns in your dataset that contains the mean and sd values for a specified group, retains the rest of the dataset as-is.

## Installation

b2package is not yet on CRAN. But, you can download it from this repository using the following R command: 

``` r
# install.packages("devtools")
devtools::install_github("stat545ubc-2021/b2packagetessosbrn", ref = "0.1.0")
```

<!-- And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("stat545ubc-2021/functions-tessosbrn")
```
--> 

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(b2package)
mean_sd(palmerpenguins::penguins, island, body_mass_g)
```

This package is useful because it allows those cleaning their datasets to have simple functions that provide useful columns without dealing with tidyverse steps

